\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Jiayi Chen}
     {Seeking a CS internship in Software Engineering, AI, ML, Robotics for Summer/2019 or a Full-time job in 2020}
\section{Experience}

\begin{eventlist}

\item{September 2018 -- Current}
     {University of California, Berkeley}
     {Game Theory Researcher}

Participate in the GamesCrafters research and development group, directed by Dr. Garcia, to explore the fertile area of combinatorial and computational game theory. We solve, play and analyze two-person, abstract strategy games.

\item{January 2018 -- May 2018}
     {University of California, Berkeley}
     {EE 16B Lab Assistant}
%Michel Maharbiz
     
Teach students to design, build and debug circuits, as well as drawing electrical schematics, understand and apply concepts of ADC, DAC, filter, K-mean cluster, feedback control, as well as machine learning algorithms--SVD and PCA during undergraduate lab sessions;

Guide students to work on an EE project -- a voice demand robotic car which goes through a cycle of listening, classifying, identifying and moving.


\item{March 2018 -- April 2018}
     {CS 61B, University of California, Berkeley}
     {BearMaps Project}

Implement a web mapping application where users can open an HTML file in their web browser that display a map of the city of Berkeley. With the given front end, my task is to write the back end - the web server that powers the API that the front end makes requests to. The interface supports scrolling, zooming, and shortest route finding. My back end code does all the work of figuring out what image data to display and finding the shortest path between the two selected locations.

\item{January 2017 -- May 2017}
     {CS 30, El Camino College}
     {DiggerMan Project}

Implement a game application called DiggerMan in C++ by using visual studio platform with two other teammates and my role was to manage the game characters’ functionality.

\item{September 2016 -- June 2017}
     {MESA Center, El Camino College}
     {Physics Teaching Assistant}

Tutor groups of students in understanding concepts and problem solving. Topics covered are “Mechanics of Solids”, “Fluids, Heat and Sound”, “Electricity and Magnetism” and “Optics and Modern Physics.”\smallskip\\

Grade homework sets for two physics courses taught by Dr. Eyal Goldmann. Provide insightful and useful feedback for students to have a better understanding of the materials, incorporate more organization than their previous work.

\end{eventlist}

\personal
    {(424) 212-2408}
    {jiayi\_chen@berkeley.edu}
%https://www.linkedin.com/in/jiayi-chen-aptx4869/

\section{Education}
     


\item\fontsize{12pt}\selectfont\textbf{University of California, Berkeley}
     {\smallskip\newline B.S. Electrical Engineering \& Computer Science}
     {\smallskip\newline Regents' and Chancellor's Merit Scholarship}
     {\smallskip\newline Expected: December 2019, GPA 3.614}
     
\item\fontsize{12pt}\selectfont\textbf{El Camino College, Torrance, CA}
     {\smallskip\newline Computer Science Certificate}
     {\smallskip\newline Jan 2015 -- May 2017, GPA 3.879}


\section{Course Work}
\begin{tabular}{rll}
CS 188&Artificial Intelligent (In Progress)\\
EECS 106A&Robotics (In Progress)\\
EECS 127&Optimization Models (In Progress)\\
CS 189 & Machine Learning (Plan)\\
CS 170 & Efficient Algorithms and Intractable\\
    &   Problems (Plan)\\
CS 61A  &   The Structure and Interpretation of\\
        &   Computer Programs (Python, SQL, \\
        &   Scheme)\\
CS 61B  &   Data Structures\\
CS 61C  &   Computer Architecture\\
CS 70   &   Discrete Mathematics and Probability\\
CS 1&Problem Solving \& Program Design\\
    &   using C++\\
CS 3& Computer Programming in Java\\
CS 30&Advance Programming in C++\\
EE 16A\&B    &   Designing Information Devices\\
        &   and System I\&II\\
EE 120  &   Signal and System
\end{tabular}

\section{Skills}

Python \textbullet{} Java \textbullet{} C/C++ \textbullet{} SQL \textbullet{} Assembly\smallskip\\
HTML \textbullet{} CSS \textbullet{} MapReduce \textbullet{} Spark \textbullet{} OpenMP\smallskip\\
Robot Operation System (ROS) \textbullet{} Linux \textbullet{} Git \smallskip\\ Object-Oriented Programming (OOP)\smallskip\\
TensorFlow \textbullet{} Debugging \textbullet{} Circuit Design\smallskip\\
Signal and System \textbullet{} Feedback Control
%Python,Java,C/C++,SQL,Assembly,HTML,CSS,MapReduce,Spark,OpenMP,Robot Operation System (ROS),Linux,Git,Object-Oriented Programming (OOP),TensorFlow,Debugging,Circuit Design,Signal and System,Feedback Control

\section{Awards and Honors}
\begin{tabular}{rll}
Sept 2017 & Member of Tau Beta Pi National\\
&Engineering Honor Society \medskip\\
April 2017 & Regents and Chancellor’s Scholarship\\
&(Top 2\% of incoming students)\medskip\\
June 2017 & Jack Vedder Mathematic Scholar\medskip\\
Nov 2016 & AMATYC (American Mathematical\\
&Association of Two-Year College)\\
&Contest 1\textsuperscript{st} Place in El Camino College
\end{tabular}



\end{document}
